The FAIRification of research in real-world evidence: A practical introduction to reproducible analytic workflows using Git and R

### 2023-11-23 manuscript/manuscript.qmd
adjusted word count
corrected typo

[**Word count:**]{.underline} 3,336 words

@@

In case a users wants to join or contribute to an already existing project, `git clone` works the same way with the only difference that the repository already contains some files and is not empty.

>>>>

[**Word count:**]{.underline} 4,293 words

@@

In case a user wants to join or contribute to an already existing project, `git clone` works the same way with the only difference that the repository already contains some files and is not empty.
